---
title             : "Full-day, in home validation of infant body position measurements from inertial sensors"
shorttitle        : "Infant position in the home"

author: 
  - name          : "John M. Franchak"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "UC Riverside Department of Psychology, 900 University Avenue, Riverside, CA 92521"
    email         : "franchak@ucr.edu"
  - name          : "Maximilian Tang"
    affiliation   : "1"
  - name          : "Hailey Rousey"
    affiliation   : "1"
  - name          : "Chuan Luo"
    affiliation   : "1"
      
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Abstract
  
keywords          : "body position, motor development, everyday experiences, sitting, machine learning"
wordcount         : "X"

bibliography      : "master.bib"

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
csl               : apa.csl
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \raggedbottom
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library("papaja")
library(knitr)
library(patchwork)
library(tidyverse)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Current 

# Methods

## Participants

## Apparatus

## Procedure

## Body position annotation

## Body position classification

# Goal 1: Optimize and validate body position classification model
<!--resampled-metrics, splithalf-metrics, predictions CSVs generated from tune_ml/classification_tidymodels.R -->

# Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement.csv, generated from analysis-pt2/compile_agreement.R -->

# Goal 3: Compare classification estimates to prior literature
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->

# Goal 4: Examine wear time and compliance in full-day data collection
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
